Bayesian hidden Markov model analysis of single-molecule force spectroscopy:\\ Characterizing kinetics under measurement uncertainty

### 2015-02-21 manuscripts/bayesian-hmm-method/bhmm.tex

\begin{figure*}[tbp]
\noindent
\resizebox{\textwidth}{!}{\includegraphics{fiber3-trace11-mlhmm-stateassignments}}
\caption{{\bf Experimental force trajectory of %the p5ab 
{\color{red} an RNA} hairpin and MLHMM state assignments.}
Observed samples are colored by their hidden state assignments.
Dark horizontal lines terminating in triangles to the right denote state means, while lightly colored bands indicate one standard deviation on either side of the state mean.
The gray histogram on the right side shows the total observed probability of samples, while the colored peaks show the weighted Gaussian output contribution from each state, and the black outline the weighted sum of the Gaussian output contributions from the HMM states.
\label{figure:p5ab-observed-trajectory}}
\end{figure*}

>>>>

\begin{figure*}[tbp]
\noindent
\resizebox{\textwidth}{!}{\includegraphics{fiber3-trace11-mlhmm-stateassignments}}
\caption{{\bf Experimental force trajectory of {\color{red} an RNA} hairpin and MLHMM state assignments.}
Observed samples are colored by their hidden state assignments.
Dark horizontal lines terminating in triangles to the right denote state means, while lightly colored bands indicate one standard deviation on either side of the state mean.
The gray histogram on the right side shows the total observed probability of samples, while the colored peaks show the weighted Gaussian output contribution from each state, and the black outline the weighted sum of the Gaussian output contributions from the HMM states.
\label{figure:p5ab-observed-trajectory}}
\end{figure*}
